### 2019-10-02 paper/paper.tex
Wraps paper to 78 chars. Adds some analysis code

Changes in axon brtanching density are assumed to depend also on the influence of guidance molecules and on the density of branches at adjacent cortical locations:

@@

>>>>

Changes in axon branching density are assumed to depend also on the
influence of guidance molecules and on the density of branches at
adjacent cortical locations:

@@

\subsection*{}

\subsection*{Relative interaction strengths}

One possibility is to modify the strength of the guidance interactions of the
two, orthogonal guidance gradients. In the simulation we modify the magnitude
of the expression of each guidance molecule, although this is equivalent to,
and could stand for a more or less vigourous movement of axons in response to
un-modified guidance gradients.
